What Determines House Prices in Ames, Iowa

### 2022-07-31 Final Draft/paper.tex
Paper additions finished

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{ {./images/} }
\usepackage{float}
\usepackage{multirow}
\title{What Determines House Prices in Ames, Iowa}
\author{Bryan Klee and Joe Lucas}
\date{July 31st, 2022}
\begin{document}
	\maketitle
	\section{Abstract}
	Add this at the end

@@

	\subesction{Data Prep & Standardization}

@@

	\begin{enumerate}
		\item Neighborhood
		\item[\textbullet] 25: One for each neighborhood
		\item Overall Quality
		\item[\textbullet] 10: One for each rating 1 - 10.
		\item Overall Condition
		\item[\textbullet] 10: One for each rating 1 - 10.

@@

	Table Here

@@

	Table Here

@@

@@

	Insert formula Here

@@

	Insert subpolotted graph.

@@

	Insert formula here

@@

	Insert Subplotted graph here

	The LASSO Regression model dropped 3 of the 52 features, those being: Lot Frontage, Neighborhood_SWISU, and OverallCond_5. This comes as no surprise as again the most highly weighted features were the Overall Quality and Overall Condition scores at each end of the rating scale. Additionaly, recall that the MLR found that Lot Frontage was not significant, so that could explain why LASSO reduced it to 0.

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{ {./images/} }
\usepackage{float}
\usepackage{multirow}
\title{What Determines House Prices in Ames, Iowa}
\author{Bryan Klee and Joe Lucas}
\date{July 31st, 2022}
\begin{document}
	\maketitle
	\section{Abstract}
	With inflated home prices as a result of the pandemic, it is hard to tell nowadays what is the true reason for a home's value. This study set out to determine if Location, Size, Condition, Quality, and Age are the true main factors in determining a home's price. With home sales data collected from homes in Ames, Iowa between the years 2006-2010, we set out to create a model which would tell us just that. While there were many features at our disposal to explore, our goal was to answer the main question, "Do Location, Size, Condition, Quality, and Age affect home prices?" So, we did just that by only including features in this study which related to those five factors. Three different models, were produced: Multiple Linear Regression, Ridge Regression, and LASSO Regression. All three models were chosen because of their ability to predict home price, while also telling us which factors were the most important. While all three models explained about 91 percent of the variance in home price, they confirmed our suspicians. Overall Quality and Condition are the most influential factors in the price of a home, followed by Location, Size, and Age. For rankings of Quality and Condition, it is only the rankings at the ends of the spectrum (1-3 and 8-10) that affect the home's price the most. This study should be expaned to include more miscellaneous variables that might have a hidden significant effect on the price of a home.

@@

	\subsection{Data Prep and Standardization}

@@

	\begin{enumerate}
		\item Neighborhood
		\item[\textbullet] 25: One for each neighborhood
		\item Overall Quality
		\item[\textbullet] 10: One for each rating 1 - 10.
		\item Overall Condition
		\item[\textbullet] 10: One for each rating 1 - 10.
	\end{enumerate}

@@

	\begin{table}[]
		\centering
		\begin{tabular}{ll}
		\hline
		\multicolumn{1}{|l|}{feature} & \multicolumn{1}{l|}{VIF} \\ \hline
		LotFrontage                   & 2.29459                  \\
		LotArea                       & 2.854278                 \\
		WoodDeckSF                    & 1.244522                 \\
		GarageArea                    & 1.997873                 \\
		TotalSF                       & 3.169309                 \\
		TotalPorchSF                  & 1.272145                 \\
		TotalBaths                    & 2.113038                 \\
		YearsOld                      & 7.157472                
		\end{tabular}
		\end{table}

@@

	\begin{table}[]
		\centering
		\begin{tabular}{lllllll}
		\hline
		\multicolumn{1}{|l|}{Feature}    & \multicolumn{1}{l|}{coef} & \multicolumn{1}{l|}{std err} & \multicolumn{1}{l|}{t} & \multicolumn{1}{l|}{P\textgreater{}|t|} & \multicolumn{1}{l|}{{[}0.025} & \multicolumn{1}{l|}{0.975{]}} \\ \hline
		Lot Frontage                     & 0.0007                    & 0.006                        & 0.122                  & 0.903                                   & -0.011                        & 0.012                         \\
		Lot Area                         & 0.0575                    & 0.006                        & 8.991                  & 0                                       & 0.045                         & 0.07                          \\
		Wood Deck SF                     & 0.0094                    & 0.004                        & 2.221                  & 0.027                                   & 0.001                         & 0.018                         \\
		Garage Area                      & 0.0416                    & 0.005                        & 7.779                  & 0                                       & 0.031                         & 0.052                         \\
		Total SF                         & 0.1208                    & 0.007                        & 17.927                 & 0                                       & 0.108                         & 0.134                         \\
		Total Porch SF                   & 0.0165                    & 0.004                        & 3.875                  & 0                                       & 0.008                         & 0.025                         \\
		Total Baths                      & 0.0532                    & 0.006                        & 9.66                   & 0                                       & 0.042                         & 0.064                         \\
		Years Old                        & -0.0974                   & 0.01                         & -9.614                 & 0                                       & -0.117                        & -0.077                        \\
		Neighborhood Bloomington Heights & 1.9433                    & 0.035                        & 55.257                 & 0                                       & 1.874                         & 2.012                         \\
		Neighborhood Bluestem            & 1.9833                    & 0.119                        & 16.639                 & 0                                       & 1.749                         & 2.217                         \\
		Neighborhood Briardale           & 1.9228                    & 0.044                        & 44.018                 & 0                                       & 1.837                         & 2.008                         \\
		Neighborhood Brookside           & 1.9465                    & 0.023                        & 85.246                 & 0                                       & 1.902                         & 1.991                         \\
		Neighborhood Clear Creek         & 1.9423                    & 0.03                         & 64.753                 & 0                                       & 1.883                         & 2.001                         \\
		Neighborhood College Creek       & 1.8809                    & 0.016                        & 118.261                & 0                                       & 1.85                          & 1.912                         \\
		Neighborhood Crawford            & 2.0665                    & 0.023                        & 91.559                 & 0                                       & 2.022                         & 2.111                         \\
		Neighborhood Edwards             & 1.844                     & 0.017                        & 106.709                & 0                                       & 1.81                          & 1.878                         \\
		Neighborhood Gilbert             & 1.88                      & 0.021                        & 90.873                 & 0                                       & 1.839                         & 1.921                         \\
		Neighborhood IDOTRR              & 1.7453                    & 0.027                        & 64.386                 & 0                                       & 1.692                         & 1.799                         \\
		Neighborhood Meadow Village      & 1.8414                    & 0.046                        & 39.816                 & 0                                       & 1.751                         & 1.932                         \\
		Neighborhood Mitchell            & 1.839                     & 0.022                        & 84.02                  & 0                                       & 1.796                         & 1.882                         \\
		Neighborhood North Ames          & 1.8943                    & 0.014                        & 138.41                 & 0                                       & 1.867                         & 1.921                         \\
		Neighborhood  Northpark Villa    & 1.9448                    & 0.051                        & 38.343                 & 0                                       & 1.845                         & 2.044                         \\
		Neighborhood Northwest Ames      & 1.8522                    & 0.019                        & 98.438                 & 0                                       & 1.815                         & 1.889                         \\
		Neighborhood Northridge          & 2.0108                    & 0.025                        & 79.557                 & 0                                       & 1.961                         & 2.06                          \\
		Neighborhood Northridge Heights  & 1.9457                    & 0.022                        & 89.016                 & 0                                       & 1.903                         & 1.989                         \\
		Neighborhood Old Town            & 1.8132                    & 0.019                        & 95.312                 & 0                                       & 1.776                         & 1.851                         \\
		Neighborhood SWISU               & 1.9037                    & 0.038                        & 49.613                 & 0                                       & 1.828                         & 1.979                         \\
		Neighborhood Sawyer              & 1.8826                    & 0.019                        & 96.571                 & 0                                       & 1.844                         & 1.921                         \\
		Neighborhood Sawyer West         & 1.869                     & 0.021                        & 90.713                 & 0                                       & 1.829                         & 1.909                         \\
		Neighborhood Somerset            & 1.9179                    & 0.02                         & 94.582                 & 0                                       & 1.878                         & 1.958                         \\
		Neighborhood Stone Brook         & 2.036                     & 0.029                        & 69.037                 & 0                                       & 1.978                         & 2.094                         \\
		Neighborhood Timerberland        & 1.8992                    & 0.027                        & 71.258                 & 0                                       & 1.847                         & 1.951                         \\
		Neighborhood Veenker             & 1.9635                    & 0.038                        & 51.042                 & 0                                       & 1.888                         & 2.039                         \\
		Overall Quality 1                & 4.8229                    & 0.06                         & 79.72                  & 0                                       & 4.704                         & 4.942                         \\
		Overall Quality 10               & 5.1388                    & 0.041                        & 125.813                & 0                                       & 5.059                         & 5.219                         \\
		Overall Quality 2                & 4.4444                    & 0.073                        & 60.932                 & 0                                       & 4.301                         & 4.587                         \\
		Overall Quality 3                & 4.5405                    & 0.031                        & 144.574                & 0                                       & 4.479                         & 4.602                         \\
		Overall Quality 4                & 4.6315                    & 0.019                        & 243.047                & 0                                       & 4.594                         & 4.669                         \\
		Overally Quality 5               & 4.6886                    & 0.013                        & 357.467                & 0                                       & 4.663                         & 4.714                         \\
		Overall Quality 6                & 4.748                     & 0.012                        & 382.295                & 0                                       & 4.724                         & 4.772                         \\
		Overall Quality 7                & 4.8053                    & 0.013                        & 358.487                & 0                                       & 4.779                         & 4.832                         \\
		Overall Quality 8                & 4.8874                    & 0.017                        & 292.007                & 0                                       & 4.855                         & 4.92                          \\
		Overall Quality 9                & 5.0612                    & 0.026                        & 197.717                & 0                                       & 5.011                         & 5.111                         \\
		Overall Condition 1              & 4.8229                    & 0.06                         & 79.72                  & 0                                       & 4.704                         & 4.942                         \\
		Overall Condition 2              & 5.2046                    & 0.059                        & 87.627                 & 0                                       & 5.088                         & 5.321                         \\
		Overall Condition 3              & 5.1532                    & 0.032                        & 161.309                & 0                                       & 5.09                          & 5.216                         \\
		Overall Condition 4              & 5.3107                    & 0.021                        & 251.545                & 0                                       & 5.269                         & 5.352                         \\
		Overall Condition 5              & 5.3378                    & 0.011                        & 477.68                 & 0                                       & 5.316                         & 5.36                          \\
		Overall Condition 6              & 5.4137                    & 0.012                        & 434.983                & 0                                       & 5.389                         & 5.438                         \\
		Overall Condition 7              & 5.4798                    & 0.014                        & 394.074                & 0                                       & 5.453                         & 5.507                         \\
		Overall Condition 8              & 5.4771                    & 0.02                         & 280.313                & 0                                       & 5.439                         & 5.515                         \\
		Overall Condition 9              & 5.5687                    & 0.033                        & 169.276                & 0                                       & 5.504                         & 5.633                        
		\end{tabular}
		\end{table}

@@

	\begin{figure}
		\includegraphics[width=\textwidth]{mlrplot}
		\caption{Residual Plots for Multiple Linear Regression}
		\label{fig:skew}
	\end{figure}

@@

	\begin{figure}
		\includegraphics[width=\textwidth]{ridgeform}
		\caption{Formula for Ridge Regression. Is the same as OLS Regression, but a shrinkage penalty is applied.}
		\label{fig:skew}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\begin{subfigure}[b]{0.4\linewidth}
		  \includegraphics[width=\linewidth]{ridgeplot}
		  \caption{Residual Plots for Ridge Regression}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\linewidth}
		  \includegraphics[width=\linewidth]{ridgefeat}
		  \caption{Most heavy feature weights as a result of Ridge Regression}
		\end{subfigure}
		\label{fig:correlation}
	  \end{figure}

@@

	\begin{figure}
		\includegraphics[width=\textwidth]{lassoform}
		\caption{Formula for LASSO Regression. Is the same as OLS Regression, but a shrinkage penalty is applied.}
		\label{fig:skew}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\begin{subfigure}[b]{0.4\linewidth}
		  \includegraphics[width=\linewidth]{lassoplot}
		  \caption{Residual Plots for Lasso Regression}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\linewidth}
		  \includegraphics[width=\linewidth]{lassofeat}
		  \caption{Most heavy feature weights as a result of LASSO Regression}
		\end{subfigure}
		\label{fig:correlation}
	  \end{figure}

	The LASSO Regression model dropped 3 of the 52 features, those being: Lot Frontage, Neighborhood SWISU, and Overall Condition 5. This comes as no surprise as again the most highly weighted features were the Overall Quality and Overall Condition scores at each end of the rating scale. Additionaly, recall that the MLR found that Lot Frontage was not significant, so that could explain why LASSO reduced it to 0.
